\tool: Revisiting BadUSB with Type-C

### 2021-01-30 WOOT/Files/discussion.tex

There exist multiple limitations of \tool.  To begin with, \tool can only gain
the information and control access of the host itself instead of external
hardware.  Consequently, as we introduced in the
Section~\ref{sec:countermeasures}, \tool can hardly bypass the defense
approaches which use external hardware for authorization.  Moreover, most of
the devices will prompt users to give authentication to the USB devices or
select one of the functional modes after they are plugged in.  Though some of
such prompts are not conspicuous for non-experts, especially when \tool is
concealed within other functional hardware such as power banks \shuqing{If
there is experiment, add it here.}, the probability whether users could get
aware that something unusual happens will increase with the existence these
prompting messages.

@@

%\shuqing{Left after experiment to finish. Will discuss from different modes
%and application scenarios.}
The USB protocol is used widely as introduced in preceding sections.  As the
technologies develop rapidly, more and more devices will be equipped with USB-C
capabilities, which makes \tool more influential.  Due to the neglection to
check the security of plugged-in USB devices of non-professional users, \tool
can be hardly detected by them while attacks are performing.  The popularity
and universality of public USB devices, including sharing power banks, even
increase such risks.  Moreover, \tool provides a better way for traditional
BadUSB attacks, since attackers can obtain the screen streaming with ease.
Attackers can use such technologies to perform more precise attacks, such as
interacting with user interface, as well as control the consequences of their
attacks.  In summary, \tool can be applied in various application scenarios and
brings rather huge impacts.

>>>>

There exist multiple limitations of \tool.  To begin with, \tool can only gain
the information and control access of the host itself instead of external
hardware.  Consequently, as we introduced in the
Section~\ref{sec:countermeasures}, \tool can hardly bypass the defense
approaches that use external hardware for authorization.  Moreover, most of
the devices will prompt users to give authentication to the USB devices or
select one of the functional modes after they are plugged in.  Though some of
such prompts are not conspicuous for non-experts, especially when \tool is
concealed within other functional hardware such as power banks \shuqing{If
there is experiment, add it here.}, the probability of whether users could get
aware that something unusual happens will increase with the existence of these
prompting messages.

@@

%\shuqing{Left after experiment to finish. Will discuss from different modes
%and application scenarios.}
The USB protocol is used widely as introduced in the preceding sections.  As the
technologies develop rapidly, more and more devices will be equipped with USB-C
capabilities, which makes \tool more influential.  Due to the neglect to
check the security of plugged-in USB devices of non-professional users, \tool
can be hardly detected by them while attacks are performing.  The popularity
and universality of public USB devices, including sharing power banks, even
increase such risks.  Moreover, \tool provides a better way for traditional
BadUSB attacks, since attackers can obtain the screen streaming with ease.
Attackers can use such technologies to perform more precise attacks, such as
interacting with the user interface, as well as control the consequences of their
attacks.  In summary, \tool can be applied in various application scenarios and
brings rather huge impacts.

### 2021-01-30 WOOT/Files/experiment.tex

\shuqing{Background is longer than real user study.}
As the functionality and effectiveness of the scripting mode and the remote control mode are rather clear, the former works similar to the original BadUSB, the latter hijacks the victim's device completely.\hongyi{I dont know if it's a good enough reason}
Here we only validate the usability of privacy extraction mode and conducted a user study.
\shuqing{10 volunteers.}
We invited 10 volunteers to participate, who are unconscious of \tool details.
Before the experiment, we disclose to the volunteers how their data might be used and request permission from both the volunteers and the institutional ethics review boards.
During the experiment, volunteers took turns to use their phones for half an hour with \tool connected, which are considered as a normal power bank.
To obtain data close to real life, they are requested to use phones just like when they use the shared power bank outside.
After the experiment, we introduced to them our attack, analyze the screen recordings together to make sure their personal data is not at risk.
\shuqing{Do we need to mention that agreement the conference required here?}
\hongyi{I'm also quite concern about this.}

\subsubsection{Result}
After collecting the videos, we analyzed the video both automatically and manually.
During the automatic analysis, we used scripts to perform OCR recognition for each frame in the recorded video and stored all of the OCR results in a database.
At last, there are 63882 pieces of data collected among 10 volunteers.
\shuqing{The data may need to be updated.}
With these results, we could learn what content the victim was browsing.
Additionally, some keywords such as \textit{account, username, and password} often appear with users' input data because they are often used as labels of input boxes.
Such keywords are more likely to lead us to user-specific data.
For example, when we searched with \textit{account} as a keyword, victim's accounts can be found in the database, as shown in the Table~\ref{tab:ocr_keyword_example}.
\shuqing{Statistics.}
The frame number is the position of this frame in the recorded video, which indicates a target for manual analysis for further data extraction.

>>>>

\shuqing{Background is longer than real user study.}
As the functionality and effectiveness of the scripting mode and the remote control mode are rather clear, the former works similar to the original BadUSB, the latter hijacks the victim's device completely.\hongyi{I dont know if it's a good enough reason}
Here we only validate the usability of privacy extraction mode and conducted a user study.
We invited 10 volunteers to participate, who are unconscious of \tool details.
Before the experiment, we disclose to the volunteers how their data might be used and request permission from both the volunteers and the institutional ethics review boards.
During the experiment, volunteers took turns to use their phones for half an hour with \tool connected, which are considered as a normal power bank.
To obtain data close to real life, they are requested to use phones just like when they use the shared power bank outside.
After the experiment, we introduced to them our attack, analyze the screen recordings together to make sure their personal data is not at risk.
\shuqing{Do we need to mention that agreement the conference required here?}
\hongyi{I'm also quite concern about this.}

\subsubsection{Result}
After collecting the videos, we analyzed the video both automatically and manually.
During the automatic analysis, we used scripts to perform OCR recognition for each frame in the recorded video and stored all of the OCR results in a database.
At last, there are 94058 pieces of data collected among 10 volunteers.
\shuqing{The data may need to be updated.}
With these results, we could learn what content the victim was browsing.
Additionally, some keywords such as \textit{account, username, and password} often appear with users' input data because they are often used as labels of input boxes.
Such keywords are more likely to lead us to user-specific data.
For example, when we searched with \textit{account} as a keyword, victim's accounts can be found in the database, as shown in the Table~\ref{tab:ocr_keyword_example}.
\shuqing{Statistics.}
The frame number is the position of this frame in the recorded video, which indicates a target for manual analysis for further data extraction.

### 2021-01-30 WOOT/Files/related_work.tex

% USB protocol attacks
In the field of USB security, protocol masquerading is also a widely used
attack scheme. Due to the lack of authentication in the USB protocol, malicious
devices can hide their real functionality with re-written
firmware~\cite{rubber,badusb,rubberducky2020,usbbypassing,iseeyou,usbdriver}.
These works rewrite the firmware of a normal-looking flash drive, which allows
it to pretend like other devices. When these modified drives are connected to the
host, they could be recognized as a keyboard or mouse. Then the attacker can
execute malicious payloads as they were using the victim's devices. Due to the
limitation of USB 2.0~\cite{usb20} protocol, these BadUSB
attacks~\cite{badusb} are unable to obtain video feedback from the victim
as video was not supported until USB 3.0~\cite{usb30}. Though USB 2.0 does not
support video transmission, there exists a protocol called MHL (Mobile
High-Definition Link) which extends the USB standard and allows the video signal to
be transmitted through the USB interface. JFC~\cite{JFC}, short for juicy filming
charging is such a work that abuses this standard and exfiltrate video data
from the victim without permission. But in JFC, this data exfiltration is not
combined with BadUSB attacks and MHL is an outdated standard, which limits its
capability.

@@

% Using USB for information leakage
As a data transmission protocol, USB inevitably leaks electromagnetic signals
to the environment which may contain sensitive information. Leveraging this
physical phenomenon, previous works~\cite{smartphone,
poweremi,revealing,su2017usb,usbgpslocator,bates2014leveraging,badusbhub,usbfinger,side,usbdriver}
eavesdrop on leaked signals and recover the sensitive data. In a similar fashion,
\cite{usbee,turnip} emit electromagnetic emissions by data injection on the bus
with the connected USB devices as an RF transmitter and \cite{usbkiller,cable}
inject analog
power to cause physical damage to the host machine. Even though the data,
including the video data, could be recovered in this way, these attacks for
executing malicious code are too difficult to work, and the invisibility is a
problem that cannot be ignored due to the spatial locality of radio frequency.

@@

To solve this flaw, GoodUSB~\cite{tian2015defending} reports the functionality claimed
by the device to the user and let the user decides whether to authorize. When a device
is plugged in, GoodUSB will load its driver but limit its functionality until a
series of authorizations are completed. These authorizations are designed to be
performed manually. As BadUSB is normally unable to obtain the video stream of
the host, an attacker cannot complete this authorization with
an automatic script. Thus this defense is sufficient for normal BadUSB attack. But
if the attacker has the access to victim's screen, GoodUSB will be bypassed
easily as the attacker can just complete this authorization manually and
perform subsequent attacks.

After the USB enumeration and driver loading, some related works
trying to archive `defense in depth'
against BadUSB attack.  Neuner et 
al.~\cite{neuner2018usblock}
prevents BadUSB attacks from the malicious flash drive by analyzing
the temporal characteristics of BadUSB-like attacks. This defense mechanism is
effective because the attacker cannot obtain the screen of the host using
BadUSB. In this case, the malicious device can only inject key stoke in a very
short time to reduce the risk of being discovered. This defect causes the
typing characteristics of BadUSB to be detectable. Pham et
al.~\cite{pham2010optimizing} optimize windows security features. It can
block the execution of unsigned files and the installation of unsigned drivers
carried on portable media. Moreover, in GoodUSB, a VM is deployed in the host to as
a honeypot to detect and stop malicious behavior of USB devices.

@@

To summarize, there exists a clear trade-off between the effectiveness and the
plug-and-play property. Though hardware disabling solutions like USB Condom
archives almost absolute security, the functionality of USB is scarified.
Other solutions like GoodUSB or whitelist are either bypassable or insufficient
under certain cases.  Some vendors may sacrifice defensive capabilities to
improve the usability, which allows attackers to take advantage of.

>>>>

% USB protocol attacks
In the field of USB security, protocol masquerading is also a widely used
attack scheme. Due to the lack of authentication in the USB protocol, malicious
devices can hide their real functionality with re-written
firmware~\cite{rubber,badusb,rubberducky2020,usbbypassing,iseeyou,usbdriver}.
These works rewrite the firmware of a normal-looking flash drive, which allows
it to pretend like other devices. When these modified drives are connected to the
host, they could be recognized as a keyboard or mouse. Then the attacker can
execute malicious payloads as they were using the victim's devices. Due to the
limitation of USB 2.0~\cite{usb20} protocol, these BadUSB
attacks~\cite{badusb} are unable to obtain video feedback from the victim
as video stream was not supported until USB 3.0~\cite{usb30}. Though USB 2.0 does not
support video transmission, there exists a protocol called MHL (Mobile
High-Definition Link) which extends the USB standard and allows the video signal to
be transmitted through the USB interface. JFC~\cite{JFC}, short for juicy filming
charging is such a work that abuses this standard and exfiltrate video data
from the victim without permission. But in JFC, this data exfiltration is not
combined with BadUSB attacks and MHL is an outdated standard, which limits its
capability.

@@

% Using USB for information leakage
As a data transmission protocol, USB inevitably leaks electromagnetic signals
to the environment which may contain sensitive information. Leveraging this
physical phenomenon, previous works~\cite{smartphone,
poweremi,revealing,su2017usb,usbgpslocator,bates2014leveraging,badusbhub,usbfinger,side,usbdriver}
eavesdrop on leaked signals and recover the sensitive data. In a similar fashion,
\cite{usbee,turnip} emit electromagnetic emissions by data injection on the bus
with the connected USB devices as an RF transmitter and \cite{usbkiller,cable}
inject analog
power to cause physical damage to the host machine. Even though the data,
including the video data, could be recovered in this way, these attacks for
executing malicious code are too difficult to work, and invisibility is a
problem that cannot be ignored due to the spatial locality of radiofrequency.

@@

To solve this flaw, GoodUSB~\cite{tian2015defending} reports the functionality claimed
by the device to the user and let the user decides whether to authorize. When a device
is plugged in, GoodUSB will load its driver but limit its functionality until a
series of authorizations are completed. These authorizations are designed to be
performed manually. As BadUSB is normally unable to obtain the video stream of
the host, an attacker cannot complete this authorization with
an automatic script. Thus this defense is sufficient for a normal BadUSB attack. But
if the attacker has the access to victim's screen, GoodUSB will be bypassed
easily as the attacker can just complete this authorization manually and
perform subsequent attacks.

After the USB enumeration and driver loading, some related works
trying to archive `defense in depth'
against BadUSB attack.  Neuner et 
al.~\cite{neuner2018usblock}
prevents BadUSB attacks from the malicious flash drive by analyzing
the temporal characteristics of BadUSB-like attacks. This defense mechanism is
effective because the attacker cannot obtain the screen of the host using
BadUSB. In this case, the malicious device can only inject key stoke in a very
short time to reduce the risk of being discovered. This defect causes the
typing characteristics of BadUSB to be detectable. Pham et
al.~\cite{pham2010optimizing} optimize windows security features. It can
block the execution of unsigned files and the installation of unsigned drivers
carried on portable media. Moreover, in GoodUSB, a VM is deployed in the host as
a honeypot to detect and stop malicious behavior of USB devices.

@@

To summarize, there exists a clear trade-off between the effectiveness and the
plug-and-play property. Though hardware disabling solutions like USB Condom
archives almost absolute security, the functionality of USB is sacrificed.
Other solutions like GoodUSB or whitelist are either bypassable or insufficient
under certain cases.  Some vendors may sacrifice defensive capabilities to
improve usability, which allows attackers to take advantage of.
